---
title: "AIC Model Averaging"
author: "Sarah Converse"
date: "April 4, 2020"
output: html_document
---

```{r global options, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
require(plotrix)
```
We start by using dredge() to run all possible models given the 8 predictors: `r 2^8` models. We create a table with AIC values for all possible models. 
```{r}
data <- read.csv("logitSimulatedData1April2020.csv")
data$X <- NULL

M.global <- glm(y ~ ., family = binomial, data = data)

library(MuMIn)
options(na.action = "na.fail")
AIC.table <- dredge(M.global, beta = "none", rank = 'AIC')
```
We can look at the first 4 models (they are listed by weight):  
```{r, echo = FALSE}
print(AIC.table[1:4,])
```
Next, we can extract weights for each of the set of models. We can also use the syntax 'AIC.table$weight' but this will give us the weights in descending order, whereas we are going to need them in the order the models were run.   
```{r}
models <- get.models(AIC.table, subset = TRUE)
aic <- rep(NA,dim(AIC.table)[1])
for(i in 1:length(aic)){
  model <- eval(parse(text = paste("models$`",i,"`",sep = "")))
  aic[i] <- model$aic
  exp.delta <- exp(-0.5*(aic - min(aic)))
  weights <- exp.delta/sum(exp.delta)
}
```
We print the first four weights and see that these are not in descending order as they are in the table. 
```{r, echo = FALSE}
print(weights[1:4])
```
Now we extract fitted values (predictions) from each model and calculate model-averaged predictions. 
```{r}
fitted.avg <- rep(0,length(models$`1`$fitted.values))
preds <- matrix(NA,nrow=length(aic),ncol=length(fitted.avg))
for(i in 1:length(aic)){
  model <- eval(parse(text = paste("models$`",i,"`",sep = "")))
  preds[i,] <- model$fitted.values
  fitted.avg <- fitted.avg + preds[i,]*weights[i]
}
```
We can print the first 10 of 100.  
```{r, echo = FALSE}
print(fitted.avg[1:10])
```
We can plot the first 10 model-averaged predictions for inspection. We have the model-averaged predictions in <span style="color: red;">red</span>, the global model predictions in <span style="color: black;">black</span>, and the null model predictions in <span style="color: green;">green</span>.
```{r, echo = FALSE}
plot(x = c(1:10),y = fitted.avg[1:10], col = "red", ylab = "prediction", xlab = "data point", ylim = c(0,1))
points(x = c(1:10), y = fitted(M.global)[1:10], col = "black")
points(x = c(1:10), y = fitted(null <- glm(y ~ 1, family = binomial, data = data))[1:10], col = "green")
```

Now we need to calculate the variances for the predictions. The variances need to include both the uncertainty conditional on each model *and* the model selection uncertainty. We can use bootstrapping to get the variances on the predictions for each model, but its slow. 
```{r}
sims <- 100
vars <- matrix(NA,nrow = dim(AIC.table)[1],ncol = 100)
vars.avg <- rep(0,100)
for(i in 1:nrow(vars)){
  model <- eval(parse(text = paste("models$`",i,"`",sep = "")))
  fitted <- matrix(NA,nrow = sims,ncol = 100)
  for(j in 1:sims){
    y.new <- unlist(simulate(model))
    bmod <- update(model,y.new ~ .)
    fitted[j,] <- fitted(bmod)
  }
  vars[i,] <- apply(fitted,2,var)
  vars.avg <- vars.avg + weights[i]*(vars[i,] + (preds[i,] - fitted.avg)^2)
}  
```
We can look at the first 10 of these variances.
```{r}
print(vars.avg[1:10])
```
Now we can calculate confidence intervals. 
```{r}
upper <- fitted.avg + 1.96*sqrt(vars.avg)
lower <- fitted.avg - 1.96*sqrt(vars.avg)
```
Let's also get confidence intervals on the global model.
```{r}
fitted.global <- fitted(M.global)
fits.global <- matrix(NA,nrow=sims,ncol=100)
for(j in 1:sims){
  y.new <- unlist(simulate(M.global))
  bmod <- update(model,y.new ~ .)
  fits.global[j,] <- fitted(bmod)
}
vars.global <- apply(fits.global,2,var)
upper.global <- fitted.global + 1.96*sqrt(vars.global)
lower.global <- fitted.global - 1.96*sqrt(vars.global)
```  
And we can plot the model-averaged estimates and confidence intervals alongside the estimates from the global model and confidence intervals.
```{r, echo = FALSE}
plotCI(x=c(1:10), fitted.avg[1:10], ui=upper[1:10], li=lower[1:10],xlab = "data point", ylab = "prediction",xlim = c(1,11))
par(new=TRUE)
plotCI(x=c(1:10), fitted.global[1:10], ui=upper.global[1:10], li=lower.global[1:10],xlab = "",ylab = "",col="red",xlim = c(1,11))
```